# Data Input
```{r}
training <- read.csv("pml-training.csv",header = TRUE, na.strings = c("NA", "#DIV/0!"))
testing <- read.csv("pml-testing.csv",header = TRUE, na.strings = c("NA", "#DIV/0!"))

```
# Data Cleaning
The input data has many columns with "NA" values. The following code helps in removing the columns with "NA" values greater than 90% of total number of rows. It also downselects the relevant variables for model building.
```{r}
# Missing Values
missingValues = is.na(training)
deleteColumns = which(colSums(missingValues) > 0.9 * length(training))
trainingCleanup = training[,-deleteColumns]
dim(trainingCleanup)
# Removing unwarranted variables
delete = c('X','raw_timestamp_part_1', 'raw_timestamp_part_2', 'cvtd_timestamp', 'new_window', 'num_window')
trainingFinal <- trainingCleanup[,-which(names(trainingCleanup) %in% delete)]
dim(trainingFinal)
```
# Creating subsets for training and testing the model
The training set is further divided in two sets. 1) trainingset used for building the model and 2) testset for checking the accuracy of the model built
```{r}
library(ggplot2)
library(caret)
inTrain <- createDataPartition(y=trainingFinal$classe, p=0.75, list=FALSE)
trainingset <- trainingFinal[inTrain,]
testset <- trainingFinal[-inTrain,]
```
# Random Forest
```{r}
library(randomForest)
modFit <- randomForest(classe~.,data=trainingset,importance=TRUE,ntree=100)
```
# Accuracy of the model
Confusion Matrix helps out to find the accuracy of the model
```{r}
testsetprediction = predict(modFit, newdata = testset)
confusionMatrix(testsetprediction,testset$classe)
```
~ 99.5 % is the accuracy and out of sample error is less than ~ 0.5%. This model has given excellent prediction.


#Application on test data
Applying the above model on test set to find out the classes.
```{r}
testprediction = predict(modFit,newdata=testing)
testprediction

```
#Answers

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(testprediction)
